---
title: "test"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
---

# Set up the lab

```{r setup, include=FALSE}
## Global options
rm(list=ls())
knitr::opts_chunk$set(cache = TRUE,warning=FALSE,message=FALSE)
```

```{r}
library(readxl)  # read in data
library(tidyverse) # ALL
library(sp)      # spatial
library(raster)  # spatial
library(terra)   # spatial
library(sf)      # spatial
library(tmap)    # mapping
```

# Read in our data

## Temp data

This was collected by Dr G over the course of a few weeks. The unit of analysis is a temperature reading (e.g. a single measurement of temperature at a specific time and place).  I put out 26 sensors - I actually put out a few more but I'm struggling to get them to read out.


```{r}
AllData    <- read_excel("/Users/hlg5155/Documents/GitHub/Teaching/Stat462-TempLab/Data/STAT462_TrainingData.xlsx")
AllData$DateTime <- paste(AllData$Date,"T",sprintf("%02d",AllData$Hour),":00:00",sep="")
AllData$Date <- as.Date(AllData$Date)
AllData$DateTime <-      as.POSIXct( AllData$DateTime ,format="%Y-%m-%dT%H:%M:%OS")

AllData    <- na.omit(AllData)
AllData.sf <- st_as_sf(AllData,coords=c( "X","Y"),crs="EPSG:32617")
```



## Boundry and raster data

This will be useful in making pretty plots - and assessing your output.

DR G WILL ADD IN CODE HERE


## Prediction data


DR G WILL ADD IN CODE HERE


We're also going to want to include some predictor factors.  This code will allow us to look at them

```{r}
# OK, so we want to make some summaries for each temperature sensor.
# First, let's concentrate on the things that don't change - so I'll call it meta data
# e.g. the data about each point rather than our response.
# These are things that don't change with time

StationInfo <- AllData.sf %>%
  group_by(Serial) %>%
  summarise(TownshipName = first(TownshipName),
            Elevation = first(Elevation_1m),
            Slope = first(Slope_1m),
            Roughness = first(Roughness_1m),
            Aspect = first(Aspect_1m),
            LandCover_Code = first(LandCover_Code),
            NCLD_Percent_Tree_Cover = first(NCLD_Percent_Tree_Cover),
            NCLD_Percent_Concrete = first(NCLD_Percent_Concrete),
            DistRoad = first(DistanceToRoad)) %>%
  arrange(Serial, .locale = "en")

NumberStations <- nrow(StationInfo)

```


# Checking each station


```{r}
# change n for different stations
n=1

# plot
   StationData <- AllData[which(AllData$Serial %in% StationInfo$Serial[n]),]
   plot(StationData$Temp_F ~ StationData$DateTime, type="h",
        main=paste("Sensor:",StationData$Serial[1]),
        xlab="Date/Time",ylab="Temperature(F)")
   
# summarise
StationSummary <- StationData %>%
  group_by(Date) %>%
  summarise(MinTemp = min(Temp_F),
            MaxTemp = max(Temp_F)) %>%
  arrange(Date, .locale = "en")


# filter as needed
DarkData <- StationData[which(StationData$Light_Lux <= 0),]
StationQC <- DarkData[which(DarkData$Temp_F < 50),]

# Replot
   plot(StationQC$Temp_F ~ StationQC$DateTime, type="h",
        main=paste("Sensor:",StationData$Serial[1]),
        xlab="Date/Time",ylab="Temperature(F)")
   


```


```{r}


```


